---
title: "Vignette - Users guide to spectralanalysis"
author: "Dirk F Moore"
date: "5/23/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to spectral count data

This package is designed to compare protein spectral count data derived from an experiment comparing two samples.

## Installing the `spectralanalysis` package

This package requires the `qvalue` package in Bioconductor. The following commands check for the presence of the Bioconductor installation facility

```{r, echo=TRUE}
if (!requireNamespace("BiocManager", quietly = TRUE))
install.packages("BiocManager")
```

Now install the `qvalue` package from Bioconductor:

```
BiocManager::install("qvalue")
```

Since the `spectralanalysis` package is on github, before installing it we must install the `devtools` package from CRAN, by typing

```
install.packages("devtools")
```

Then install the `spectralanalysis` package from the github repository by typing

```
devtools::install_github("mooredf22/spectralanalysis")
```

We also will need the `Hmisc` package:

```
install.packages("Hmisc")
```

Now attach the `spectralanalyze`, `qvalue`, and `Hmisc` packages:

```{r, echo=TRUE}
library(spectralanalysis)
library(qvalue)
library(Hmisc)
```

We may inspect the data set `spectralData_ClN1_late` as follows:

```{r, echo=TRUE}
str(spectralData_CLN1_late)
```

We may examine the names as follows:

```{r, echo=TRUE}
names(spectralData_CLN1_late)
```
Now we may extract the values for animal 1 as follows:

```{r, echo=TRUE}
clnWt1 <- spectralData_CLN1_late[,c(1,2,8)]
head(clnWt1)
proteincount <- clnWt1 
```


Give a list of odds (and odds ratios) to test as null hypotheses:

```{r, echo=TRUE}
odds.list <- c(1,2)
```

Now compare the cln and wt groups:

```{r, echo=TRUE}
result <- proteinCountCompare(proteincount)
```
The function returns a list of data frames:
1. Wilson 95% confidence intervals
2. P-values for each protein based on a binomial comparison
3. Q-values for these
4. P-values for each protein based on Fisher's exact test
5. Q-values for these

```{r, echo=TRUE}
names(result)
head(result$wilson.AB)
head(result$pval.AB)
head(result$qval.AB)
head(result$fisher.odds)
head(result$pval.AB.f)
head(result$qval.AB.f)
```

```{r, echo=TRUE}
protein.mult.pval <- data.frame(proteincount," ",result$wilson.AB," ",result$pval.AB," ",
            result$qval.AB," ",result$fisher.odds," ",
            result$pval.AB.f," ",result$qval.AB.f)
head(protein.mult.pval)
```

We may write out the results to an external directory as follows:
```
setwd("c:\\temp")
write.csv(protein.mult.pval,file="Cln1Wt1.csv", row.names=F)
```

